Towards a Sound and Complete Library for Modal Logics Reasoning in Coq

### 2022-06-19 paper/paper.tex
Adding abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  The correct specification of requirements is crucial for software development.
  Modal logics are ...
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  This work describes an encoding of modal logics using the Coq proof assistant.
  Our formalization differs from previous attempts by providing a uniform
  representation of several systems for modal logics, using Coq's rich type
  structure. We illustrate the usefulness of our library in a formalization of
  L\"ob's theorem, which closely follows a classical proof of this result.
\end{abstract}
